---
title: "Love vs extraterrestials"
author: "Kim Godfrey"
date: "Spring 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
help("m111surveyfa13")
mydata<-m111surveyfa13 <- na.omit(m111surveyfa13)
```

# A question of Belief

Your data is in the dataframe called "mydata" examine it in the environment tab  
do a variable analysis on the 3 Questions and then upload the appropriate Rmd template for this job.   
Also create an empty github repository called "Belief" and make it the remote repository for  
this assignment.  For each question supply graphical evidence, numerical summaries, an inferential test, and a conclusion.  When finished push your rmd file, your project file, and your knitted html file to your github repo.  Finally turn in to Canvas the link to your github repo.




# Your First Question  

### Do people who believe in Love at First sight also tend to believe in Life on other planets?

$H_0$: There is no relation between belief in love at first and belief in life on other planets

$H_A$: There is a relationship between belief in love at first sight and belief on other planets



 Graphic display 

```{r}
barchartGC(~love_first + extra_life,data=mydata, xlab="love @ first sight")
```

People who believe in love at first sight also tend to believe in life on other planets

Numerical summary

```{r}
table1 <- xtabs(~love_first + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```
looks about the same

Inference
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

We fail to reject the hypothsis because the p value is higher than 0.05


# Your second Question  

### Is there a difference between boys and girls with respect to belief in life on other planets?

$H_0$: There is no relation between boys and girls with respect to life on other planets

$H_A$: There is a relation btween boys and girls with respect to life on other planets

 
Graphical summary  
 
```{r}
barchartGC(~sex+ extra_life,data=mydata)
```

Boys believe there is life on other planets



Numerical summary

```{r}
table1 <- xtabs(~sex + extra_life, data=mydata)
rowPerc(table1)
colPerc(table1)
```

Looks about the same


Inference

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

We fail to reject the hypothis because the p value is higher than 0.05




# Your last Question   

### Is there a difference between boys and girls with respect to belief in love at First sight?

$H_0$: There is no relation between boys and girls with respect to love at first sight

$H_A$: There is a relation between boys and girls with respect to love at first sight


Graphical summary

```{r}
barchartGC(~sex + love_first,data=mydata)
```
Boys do not believe in love at first sight over girls


Numerical summary

```{r}
table1 <- xtabs(~sex + love_first, data=mydata)
rowPerc(table1)
colPerc(table1)
```

Girls believe in love at first sight over boys


Inference

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
We fail to reject the hypothis becsuse the p value is higher than 0.05
